\sysfull

### 2017-07-28 paper/intro.tex
Intro revised - ready for Brandon to re-read it

While promising, energy-harvesting devices present a unique design challenge in
that they operate only {\em intermittently} when energy is available~\cite{hicks_isca_2017,lucia_snapl_2017}. An
energy-harvesting device buffers energy from its environment, e.g., in a
capacitor~\cite[Fig. 3]{gorlatova_tmc_2013},~\cite[Fig. 1]{gunduz_commag_2014}. When a threshold quantity of energy accumulates, the device begins operating. Harvestable energy sources typically produce relatively very little power compared to a platform's operating power level---compare for instance~\cite[Table III and V]{prasad_comst_2014} with~\cite[Table I]{carrano_cst_2014}. A devices operates for a brief period of time and when buffered energy is depleted, shuts down and begins recharging to operate again later. As an example, inter-task time may even exceed 20\,s for wireless energy-harvesting battery-less vivo digestive tract monitoring system~\cite[Fig. 3c]{nadeau_naturebio_2017}. On top of that, charge and discharge times vary by device and some of them~\cite{wisp} may fail $\approx$10 to $\approx$100 times per second~\cite[Fig. 1]{tan_infocom_2016},~\cite[Fig. 1]{mementos},~\cite[Fig. 3]{nvp}.

\todo{Put reference for "tictpl" somewhere}{Brandon}

@@

%FRAM costs more than FRAM -- need to figure out how to execute out of SRAM

@@

%Task sizing is hard -- how to chop without risking inefficiency or non-term

@@

To answer these, in this work we develop {\bf \sys}: a new programming and execution model that utilizes two new runtime features: {\em dynamic task coalescing} to efficiently execute tasks without exceeding available energy (answering question (i)) and  {\em volatile memory virtualization} to leverage efficient volatile memory (answering question (ii)). \sys's novel memory virtualization mechanism uses a device's SRAM as the working memory during a task's execution, populating the SRAM with a page of data from FRAM as necessary at the start of the task. At the end of the task, the SRAM is committed back to FRAM using efficient DMA block copies~\cite{kistler_micro_2006}. When a task accesses data outside of a page in SRAM, the task must fetch data from FRAM.

\todo{articulate this last point better}{Przemek}

With this paper we provide the following list of contributions.
%
\begin{enumerate}
%
\item {\bf Task coalescing mechanism:} \sys's core contribution is the introduction of dynamic task coalescing mechanism. It allows the programmer or a compiler to intuitively decompose the program into small tasks that amortize fixed per-task overheads, yet present no risk of exceeding device energy capacity. As such a decomposition executes, \sys~{\em coalesces dynamically} consecutive tasks. Coalescing elides the commits of coalesced tasks by buffering multiple tasks' updates in an FRAM commit buffer. Periodically, as the span of the coalesced task grows, \sys ends coalescing and commits the state of the coalesced task. If a power failure interrupts a sequence of coalesced tasks, \sys adaptively reduces the number of tasks in that sequence that it will coalesce, committing sooner in future executions. Consequently, \sys's coalescing mechanism allows a program to execute efficiently across a range of energy buffer sizes, avoiding transition overheads in larger buffers, and ensuring progress in smaller buffers.
%
\todo{Provide numerical results for this section}{Przemek}
\todo{Mention automatic task generation}{Przemek}
%
\item {\bf Evaluation of data swapping strategies:} We propose and explore two data swapping strategies for intermittently-powered systems based on FRAM/SRAM architecture. The first strategy is {\em demand paging}, which swaps the SRAM page with a new page from FRAM, buffering the swapped-out page until commit. The second strategy is {\em buffered direct access}, which directly reads and writes FRAM relying on dynamic double-buffering to ensure memory is consistent at
commit. 
%
\todo{Once paging is fully implemented--update the paragraph}{Przemek}
\todo{Provide numerical results for this section}{Przemek}
%
\item {\bf Extensive \sys evaluation:} We evaluated \sys on a collection of benchmark programs~\cite[Sec. 5]{chain}, and compare directly to state-of-the art task-based runtime~\cite{chain}, showing that \sys has high performance and can flexible target a variety of platforms without recompiling the code. We further demonstrate the efficiency and versatility of \sys with an end-to-end evaluation of a sensing and data processing application deployed in a lab environment. 
%
\todo{add detailed text about evaluation results}{Przemek}
%
\end{enumerate}

>>>>

While promising, energy-harvesting devices present a unique design challenge in
that they operate only {\em intermittently} when energy is available~\cite{hicks_isca_2017,lucia_snapl_2017}. An
energy-harvesting device buffers energy from its environment, e.g., in a
capacitor~\cite[Fig. 3]{gorlatova_tmc_2013},~\cite[Fig. 1]{gunduz_commag_2014}. When a threshold quantity of energy accumulates, the device begins operating. Harvestable energy sources typically produce relatively very little power compared to a platform's operating power level---compare for instance~\cite[Table III and V]{prasad_comst_2014} with~\cite[Table I]{carrano_cst_2014}. A devices operates for a brief period of time and when buffered energy is depleted, shuts down and begins recharging to operate again later. As an example, inter-task time may even exceed 20\,s for wireless energy-harvesting battery-less vivo digestive tract monitoring system~\cite[Fig. 3c]{nadeau_naturebio_2017}. On top of that, charge and discharge times vary by device and some of them~\cite{wisp} may fail $\approx$10 to $\approx$100 times per second~\cite[Fig. 1]{tan_infocom_2016},~\cite[Fig. 1]{mementos},~\cite[Fig. 3]{nvp}.
%
\todo{Put reference for "tictpl" somewhere}{Brandon}

@@

@@

@@

To answer the above, in this work we develop {\bf \sys}: a new programming and execution model that utilizes two new runtime features: {\em dynamic task coalescing} to efficiently execute tasks without exceeding available energy (answering question (i)) and  {\em volatile memory virtualization} to leverage efficient volatile memory (answering question (ii)). \sys's novel memory virtualization mechanism uses a device's SRAM as the working memory during a task's execution, populating the SRAM with a page of data from FRAM as necessary at the start of the task. At the end of the task, the SRAM is committed back to FRAM using efficient DMA block copies~\cite{kistler_micro_2006}. When a task accesses data outside of a page in SRAM, the task must fetch data from FRAM.
%
\todo{articulate this last point better}{Przemek}

With this paper we provide the following list of contributions.
%
\begin{enumerate}
%
\item {\bf Task coalescing mechanism:} \sys's core contribution is the introduction of dynamic task coalescing mechanism. It allows the programmer or a compiler to intuitively decompose the program into small tasks that amortize fixed per-task overheads, yet present no risk of exceeding device energy capacity. As such a decomposition executes, \sys~{\em coalesces dynamically} consecutive tasks. Coalescing elides the commits of coalesced tasks by buffering multiple tasks' updates in an FRAM commit buffer. Periodically, as the span of the coalesced task grows, \sys ends coalescing and commits the state of the coalesced task. If a power failure interrupts a sequence of coalesced tasks, \sys adaptively reduces the number of tasks in that sequence that it will coalesce, committing sooner in future executions. Consequently, \sys's coalescing mechanism allows a program to execute efficiently across a range of energy buffer sizes, avoiding transition overheads in larger buffers, and ensuring progress in smaller buffers.
%
\todo{Provide numerical results for this section}{Przemek}

\item {\bf Compiler-support automatic task generation:} second \sys's core contribution is the ability to split standard C programs into \sys's compatible tasks, effectively circumventing the need for labour-intensive manual task generation of the state of the art solutions~\cite{chain,alpaca}.
%
\todo{Elaborate on this more and provide numerical results}{Przemek}
%
\item {\bf Evaluation of data swapping strategies:} We propose and explore two data swapping strategies for intermittently-powered systems based on FRAM/SRAM architecture. The first strategy is {\em demand paging}, which swaps the SRAM page with a new page from FRAM, buffering the swapped-out page until commit. The second strategy is {\em buffered direct access}, which directly reads and writes FRAM relying on dynamic double-buffering to ensure memory is consistent at
commit. 
%
\todo{Once paging is fully implemented--update the paragraph}{Przemek}
\todo{Provide numerical results for this section}{Przemek}
%
\item {\bf Extensive \sys evaluation:} We evaluated \sys end-to-end on a collection of existing benchmark programs~\cite[Sec. 5]{chain} and new ones (including realistic case study of battery-less embedded sound detector) in a laboratory environment, and compare directly to state-of-the art task-based runtime~\cite{chain}, showing that \sys has high performance and can flexible target a variety of platforms without recompiling the code. 
%
\todo{add detailed text about evaluation results}{Przemek}
\todo{decide if we want to make this a contribution paragraph or not (then, put it as a closing paragraph)}{Brandon}
%
\end{enumerate}
